---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# abKeyringR

<!-- badges: start -->
[![R-CMD-check](https://github.com/code-convenience-and-ideas/abKeyringR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/code-convenience-and-ideas/abKeyringR/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/code-convenience-and-ideas/abKeyringR/branch/main/graph/badge.svg)](https://app.codecov.io/gh/code-convenience-and-ideas/abKeyringR?branch=main)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of abKeyringR is to create a few simple tools which capture required keyring entries for a project and give some guidance to building them.

This should save time and help interoperability across teams for analysis scripts which depend on "secrets".

## Installation

You can install the development version of abKeyringR like so:

``` r
# You can install thhis package directly from github
devtools::install_github("https://github.com/code-convenience-and-ideas/abKeyringR.git")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(abKeyringR)

## basic example code
abKeyringR::hello()
```
