---
title: "Checking Keyrings"
output: rmarkdown::html_vignette
description: |
    Checking keyrings is a quick investigation in how to establish needed
    keyring entries and the results of using the package to check if those
    entries are available / visible to the program.
vignette: >
  %\VignetteIndexEntry{checking_keyrings}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

This package aims to provide an easy way to process an arbitrary yaml format
that I defined to share secrets requirements for my scripts to run in different
languages. The idea was defining this template and building support in both R
and Python to check for these entries to make it easier to work between both
languages as appropriate even within the same project.

```{r setup}
library(abKeyringR)
abKeyringR::hello()
```

## Example: Loading and checking a reference yaml

This simple example loads a yaml file, and check for any missing entries
specified in that file.

```{r}
# Load an example yaml kept with the package
local_folder_yaml <- system.file("extdata", "example_keyring_entries.yaml",
  package = "abKeyringR"
)
default_email_parser <- function(x) {
  "hello"
}

loaded_keyring_entries <- abKeyringR::load_keyring_yaml(
  local_folder_yaml, default_email_parser
)

# Pull out the datasets from the yaml as a dataframe
keyring_entry_df <- abKeyringR::keyring_yaml_to_df(loaded_keyring_entries)

# Check whether the entries exist in the system and give a warning if not
resulting_missing_entries <- keyring_entry_df |>
  # Add a column for presence of entries first
  abKeyringR::check_table_entries_available() |>
  # Filter to only missing entry and return + raise warning for missing
  abKeyringR::raise_missing_entry_message()
```
